Output Summary

### 2022-01-26 03-post-process/output-plots.Rmd
Create an origin variable to use instead of c("NOR", "HOR") throughout Rmd

@@

# trib to lgr survival
new = post_subset(post, "Lphi_obs_new_Mb_Ma_dev", TRUE)
obs = post_subset(post, "Lphi_obs_Mb_Ma_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), c("NOR", "HOR"), pops)
bp = bp[,"spring-mig",,]
bp = cbind(CAT_NOR = bp[,"NOR","CAT"], CAT_HOR = bp[,"HOR","CAT"],
           LOS_NOR = bp[,"NOR","LOS"], LOS_HOR = bp[,"HOR","LOS"],
           MIN_NOR = bp[,"NOR","MIN"], MIN_HOR = bp[,"HOR","MIN"],
           UGR_NOR = bp[,"NOR","UGR"], UGR_HOR = bp[,"HOR","UGR"])
phi_Mb_Ma_bp = data.frame(
  name = rep("Spring Trap/Release to LGR", 8), pop = rep(pops, each = 2),
  origin = rep(c("NOR", "HOR"), 4), LH_type = rep("Spring Migrants", 8),
  summarize_bp(bp)
)
rownames(phi_Mb_Ma_bp) = NULL

# hydropower survival
new = post_subset(post, "Lphi_obs_new_Ma_O0_dev", TRUE)
obs = post_subset(post, "Lphi_obs_Ma_O0_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("NOR", "HOR"))
phi_Ma_O0_bp = data.frame(
  name = rep("Hydrosystem (Downstream)", 2), pop = rep("Combined", 2),
  origin = c("NOR", "HOR"), LH_type = rep("Combined", 2),
  summarize_bp(bp)
)
rownames(phi_Ma_O0_bp) = NULL

@@

# movement survival from BON to LGR
new = post_subset(post, "x_LGR_new_dev", TRUE)
obs = post_subset(post, "x_LGR_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("NOR", "HOR"))
x_LGR_bp = data.frame(
  name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
  origin = c("NOR", "HOR"), LH_type = rep("Combined", 2),
  summarize_bp(bp)
)
rownames(x_LGR_bp) = NULL

>>>>

# origin names
origins = c("NOR", "HOR")

@@

# trib to lgr survival
new = post_subset(post, "Lphi_obs_new_Mb_Ma_dev", TRUE)
obs = post_subset(post, "Lphi_obs_Mb_Ma_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], c("fall-mig", "spring-mig"), origins, pops)
bp = bp[,"spring-mig",,]
bp = cbind(CAT_NOR = bp[,"NOR","CAT"], CAT_HOR = bp[,"HOR","CAT"],
           LOS_NOR = bp[,"NOR","LOS"], LOS_HOR = bp[,"HOR","LOS"],
           MIN_NOR = bp[,"NOR","MIN"], MIN_HOR = bp[,"HOR","MIN"],
           UGR_NOR = bp[,"NOR","UGR"], UGR_HOR = bp[,"HOR","UGR"])
phi_Mb_Ma_bp = data.frame(
  name = rep("Spring Trap/Release to LGR", 8), pop = rep(pops, each = 2),
  origin = rep(origins, 4), LH_type = rep("Spring Migrants", 8),
  summarize_bp(bp)
)
rownames(phi_Mb_Ma_bp) = NULL

# hydropower survival
new = post_subset(post, "Lphi_obs_new_Ma_O0_dev", TRUE)
obs = post_subset(post, "Lphi_obs_Ma_O0_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
phi_Ma_O0_bp = data.frame(
  name = rep("Hydrosystem (Downstream)", 2), pop = rep("Combined", 2),
  origin = origins, LH_type = rep("Combined", 2),
  summarize_bp(bp)
)
rownames(phi_Ma_O0_bp) = NULL

@@

# movement survival from BON to LGR
new = post_subset(post, "x_LGR_new_dev", TRUE)
obs = post_subset(post, "x_LGR_dev", TRUE)
bp = array_format(colMeans(obs > new))
dimnames(bp) = list(all_yrs[1:dim(bp)[1]], origins)
x_LGR_bp = data.frame(
  name = rep("Hydrosystem (Upstream)", 2), pop = rep("Combined", 2),
  origin = origins, LH_type = rep("Combined", 2),
  summarize_bp(bp)
)
rownames(x_LGR_bp) = NULL
